---
title: "lvws_sensitivity_analysis"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

``` {r, include = FALSE}

source("scripts/04_analysis_intermediate.R")

```

## Loch Vale Water Chemistry Sensitivity Analysis

##### What trends exist within the data? Do these trends changed based on sampling frequency?  
Examining all post-1995 data for all major ions and parameters using both a linear and general additive model.    

Are major ions increasing in concentration in a linear manner over time? 

Are there certain months in which said increase is linear? 

##### For which months do we see linear trends? 

```{r, echo = FALSE}
library(ggplot2)

ggplot2::ggplot(data = loch_o_chem, aes(x = DATE, y = NO3_calc, color = YEAR)) +
  geom_point() + 
  geom_line() + 
  facet_wrap(~ MONTH, scales = "free", labeller = as_labeller(month_labels)) +
  geom_smooth(method = "lm") +
          stat_cor(aes(label = paste(after_stat(rr.label), ..p.label.., sep = "~`,`~")),
                       p.accuracy = 0.001, r.accuracy = 0.01, label.x.npc = "center")
```

Is a general additive model representative of the trend within the data? 





